---
title: ""
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(png)
library(imager)
library(tidyverse)
library(tximport)
library(DESeq2)
library(GenomicFeatures)
library(rtracklayer)
library(genefilter)
library(ggplot2)
library(grDevices)
library(RColorBrewer)
library(gplots)
library(ggrepel)
library(dplyr)
library(pheatmap)
library(plotly)
library(heatmaply)
library(tidyverse)
```

# PCA {.tabset}

We discussed aggregating the samples P16, pCDH-empty and K36WT as a potential control to compare treated samples against (namely NSD1KO, K36M & K36R). However, it seems that the K36WT is more similar to K36R than P16 or pCDH-empty. The relationships are recapitulated in the heatmap below. 

We also see slight differences in the PCAs and heatmaps between (varianceStabilizingTransformation()) and (rlogTransformation()).

Note: pCDH indicates they're derived from over-expression experiments using pCDH lentivectors.

<details>
<summary>Size Factors</summary>
<pre>
```{r echo=FALSE}
setwd("~/testGitHub/Testing")

load("dds.RData")
load("mdat.RData")
load("vsd.RData")
load("rld.RData")

size_factors <- data.frame(estimateSizeFactorsForMatrix(counts(dds)))
names(size_factors)[names(size_factors) == "estimateSizeFactorsForMatrix.counts.dds.."] <- "Size Factor"
size_factors
```
</pre>
</details>

## vst

```{r echo=FALSE}
rv <- rowVars(assay(vsd))
select <- order(rv, decreasing=T)[seq_len(min(500,length(rv)))]
pc <- prcomp(t(assay(vsd)[select,]))
condition <- mdat$cond
scores <- data.frame(pc$x, condition)
percentage <- round(pc$sdev / sum(pc$sdev) * 100, 2)
percentage <- paste( colnames(scores), "(", paste( as.character(percentage), "%", ")", sep="") )

p <- plot_ly(scores,x=scores$PC1,y=scores$PC2,text=rownames(scores),mode="markers",color=factor(condition),marker=list(size=11))
p <- layout(p,title="",   xaxis = list(title = percentage[1]),
                 yaxis = list(title = percentage[2]))
p

```

## rlog

```{r echo=FALSE}
rv <- rowVars(assay(rld))
select <- order(rv, decreasing=T)[seq_len(min(500,length(rv)))]
pc <- prcomp(t(assay(rld)[select,]))
condition <- mdat$cond
scores <- data.frame(pc$x, condition)
percentage <- round(pc$sdev / sum(pc$sdev) * 100, 2)
percentage <- paste( colnames(scores), "(", paste( as.character(percentage), "%", ")", sep="") )

p <- plot_ly(scores,x=scores$PC1,y=scores$PC2,text=rownames(scores),mode="markers",color=factor(condition),marker=list(size=11))
p <- layout(p,title="",   xaxis = list(title = percentage[1]),
                 yaxis = list(title = percentage[2]))
p

```

# {-}

# Heatmap {.tabset}

## vst

```{r echo=FALSE}
sampleDists <- dist(t(assay(vsd[select])))
sampleDistMatrix <- as.matrix(sampleDists)
rownames(sampleDistMatrix) <- paste(vsd$cond, vsd$dir, sep="-")
colnames(sampleDistMatrix) <- paste(vsd$cond, vsd$dir, sep="-")
colors <- colorRampPalette( rev(brewer.pal(9, "Blues")) )(255)
heatmaply(sampleDistMatrix,
         clustering_distance_rows=sampleDists,
         clustering_distance_cols=sampleDists,
         col=colors)

```

## rlog

```{r echo=FALSE}
sampleDists <- dist(t(assay(rld[select])))
sampleDistMatrix <- as.matrix(sampleDists)
rownames(sampleDistMatrix) <- paste(rld$cond, rld$dir, sep="-")
colnames(sampleDistMatrix) <- paste(rld$cond, rld$dir, sep="-")
colors <- colorRampPalette( rev(brewer.pal(9, "Blues")) )(255)
heatmaply(sampleDistMatrix,
         clustering_distance_rows=sampleDists,
         clustering_distance_cols=sampleDists,
         col=colors)

```

# {-}